---
title: "Handout 1"
author: "Guillermo Gavilla, Miquel Antoni Llambías Cabot"
date: "07/11/2020"
output:  html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=8, fig.align="center", echo=TRUE, warning=FALSE, message=FALSE)
library(knitr)
library(igraph)
```

# Index

**1)** The file **facebook_sample_anon.txt** is a data table containing the list of edges of an anonymized  sample of the Facebook friendship network. Download it on your computer,  upload it to R as a dataframe, and define an undirected graph with this list of edges.

*a)* Is it connected? If it is not, replace it by its largest connected component.

*b)* Compute the edge density.

*c)* What is the mean distance among the subjects?

*d)* Calculate the list of vertices in a diameter of the graph. Plot only this path with the size of the node proportional to the degree of the node.

*e)* Calculate the shortest path from the vertex named "1000" to the vertex named "2000" in the original file.

*f)* Calculate a clique of  5 friends, if there is one.

*h)* Calculate the list of names of verteces that are the neigbours of verteces of degree one and that are not of degree one.


# Undirected Graph.

```{r}
data <- read.table("facebook_sample_anon.txt")
tail(data)
```
Load data

```{r}
graph <- graph_from_data_frame(data, directed = F)
plot(graph, edge.color = "darkgoldenrod1", edge.arrow.size = 0.001, edge.arrow.width = 1, 
     vertex.color = "cyan3", vertex.label= NA,
     vertex.size = 12, rescale = T)
```
```{r}
#graph <- make_graph(~ A-B-C-D-A, E-A:B:C:D, F-G-H-I-F, J-F:G:H:I, K-L-M-N-K, O-K:L:M:N, P-Q-R-S-P, T-P:Q:R:S, B-F, E-J, C-I, L-T, O-T, M-S, C-P, C-L, I-L, I-P, P-"0", "0"-"1")
#V(graph = graph)["A"]$name <- "1000"
#V(graph = graph)["N"]$name <- "2000"
#graph <- set_graph_attr(graph, "title", "Facebook sample anon")
#plot(graph)
```

# a) Is it connected? If it is not, replace it by its largest connected component.

```{r}
vertexConnectivityBool <- vertex_connectivity(graph, source = NULL, target = NULL, checks = TRUE)
vertexConnectivityBool
```
```{r, echo=FALSE}
if(vertexConnectivityBool > 0) {
  print("Graph is connected")
} else {
  print("Graph is not connected")
}
```

# b) Compute the edge density

```{r}
density <- edge_density(graph, loops = F)
```
```{r, echo = FALSE}
print(paste("The edge density is", density, sep = " "))
```

# c) What is the mean distance among the subjects?

```{r}
meanDistance <- mean_distance(graph, directed=F)
```
```{r, echo = FALSE}
print(paste("The mean distance is", meanDistance, "nodes", sep = " "))
```

# d) Calculate the list of vertices in a diameter of the graph. Plot only this path with the size of the node proportional to the degree of the node.

Calculate the proportional degree of the node and link the max weight of the linked nodes

```{r}
AddWeightsFromDegree <- function (graph) {
  res <- graph
  for(v in V(graph = res)$name) {
    degree <- degree(res, v)
    E(res) [ from(v) ]$weight <- degree
  }
  result <- res
}
weightedGraph <- AddWeightsFromDegree(graph)
E(weightedGraph)[from(V(weightedGraph)$name[1])]$weight
```

Calculate the diameter

```{r}
diameter <- diameter(weightedGraph, directed = FALSE)
diameterNodes <- get_diameter(weightedGraph, directed = FALSE)
```
```{r, echo = FALSE}
print(paste("The graph diameter is", diameter, "units", sep = " "))
```
```{r, echo = FALSE}
buildAdjencyGraphFromList <- function (list) {
  length <- length(list)
  res <- matrix(data = 0, ncol = length, nrow = length, dimnames = list(list$name, list$name))
  for(v in 1:length-1) {
    res[v,v+1] <- 1
  }
  result <- graph.adjacency(res, mode = 'undirected')
}
res <- buildAdjencyGraphFromList(diameterNodes)
plot(res, edge.color = "darkgoldenrod1", edge.arrow.size = 0.01, 
     vertex.color = "cyan3", vertex.label.color = "black",
     vertex.size = 21, vertex.label.cex = 0.7)
```

# **e) Calculate the shortest path from the vertex named "1000" to the vertex named "2000" in the original file.**

Graph is connected, then it exists a path between node1 = 1000 and node2 = 2000.


```{r}

vertex1 <- '1000'
vertex2 <- '2000'
paintedGraf <- graph
shortestPath <- get.shortest.paths(
        graph,
        from = V(graph)$name == vertex1,
        to = V(graph)$name == vertex2,
        weights = NULL,
        output = "vpath",
        predecessors = FALSE,
        inbound.edges = FALSE
)

E(paintedGraf, path=shortestPath$vpath[[1]])$color <- "darkgoldenrod1"
plot(paintedGraf, vertex.color = "cyan3", edge.arrow.size = 5, edge.arrow.width = 5, edge.lty=c("solid"),vertex.label = NA)


```

# f) Calculate a clique of  5 friends, if there is one.

```{r}
n <- 4
cliquesOfN <- cliques(graph, min = n, max = n)
```
```{r, echo = FALSE}
numOfCliques <- length(cliquesOfN)
if(numOfCliques > 0) {
  print(paste("There are", numOfCliques, "cliques of", n, "friends", sep = " "))
} else {
  print(paste("This graph does not feature a clique of", n, "friends", sep = " "))
}
```
```{r, echo = FALSE}
if(numOfCliques > 0) {
  print(cliquesOfN)
}
```

# h) Calculate the list of names of verteces that are the neigbours of verteces of degree one and that are not of degree one.

Get a list of degrees
```{r}
degrees <- degree(graph = graph)
degrees
```
Get only the ones with a degree equal to `1`
```{r}
filterEquals <- function (data, degree) {
  res <- NULL
  names <- data$names
  degrees <- data$degrees
  for(i in 1:nrow(data)) {
    if(degrees[i] == degree) {
      res <- append(res, names[i])
    }
  }
  result <- res
}

degreesOf1 <- data.frame(degrees, names = names(degrees))
vertexNames <- filterEquals(degreesOf1, 1)
vertexNames
```

Get neighbors of those degree 1 vertex
```{r}
getAllNeighbors <- function(graph, vertexNames) {
  res <- NULL
  for(v in vertexNames) {
    neighborsList <- neighbors(graph, v = v)
    for(n in names(neighborsList)) {
      res <- append(res, n)
    }
  }
  result <- res
}
neighborsOfDegree1 <- getAllNeighbors(graph = graph, vertexNames = vertexNames)
neighborsOfDegree1
```

Get from neighbors those with greater degree than 1
```{r}
filterGreaterThan <- function (data, degree) {
  res <- NULL
  names <- data$names
  degrees <- data$degrees
  for(i in 1:nrow(data)) {
    if(degrees[i] > degree) {
      res <- append(res, names[i])
    }
  }
  result <- res
}
degreesOfNeighbors <- degree(graph = graph, neighborsOfDegree1)
degreesOfNeighborsGreaterThan1 <- filterGreaterThan(
        data.frame(degreesOfNeighbors, names = names(degreesOfNeighbors)), 1)
degreesOfNeighborsGreaterThan1
```
